### 2014-06-08 latex/paper2.tex
typo

Heisenberg's theory was strange to physicists because the order in which
matrices are multiplied matters, $a$ times $b$ could be different from
$b$ times $a$, so that $ab - ba$ is not zero..  This $ab - ba$ caught
Dirac's attention, as Dirac was familiar with this noncommuting
multiplication from his mathematics training, but did not understand its
physical significance or implications. Always interested in relativity,
Dirac also tried to create a relativistic version of Heisenberg's theory
but had no success and soon gave up.

>>>>

Heisenberg's theory was strange to physicists because the order in which
matrices are multiplied matters, $a$ times $b$ could be different from
$b$ times $a$, so that $ab - ba$ is not zero. This $ab - ba$ caught
Dirac's attention, as Dirac was familiar with this noncommuting
multiplication from his mathematics training, but did not understand its
physical significance or implications. Always interested in relativity,
Dirac also tried to create a relativistic version of Heisenberg's theory
but had no success and soon gave up.
